\Title

### 2021-01-26 manuscript/manuscript.tex
Review the window size results

\begin{equation}
    \left[
      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
    \right]
    \hat{\mathbf{m}} =
    \mathbf{B}\trans\mathbf{W}
    \mathbf{d}^o.
\end{equation}

@@

\subsection{Comparison of source distribution strategies}

@@

\subsection{Performance and accuracy of gradient boosting}

Our second goal is to assess the accuracy of the predictions achieved by the
gradient boosting algorithm while registering its performance by comparison
with the non-boosted equivalent sources.

@@

One factor that plays an important role on the performance of the gradient
boosted equivalent sources is the size of the overlapping windows used to create
each set of equivalent sources.
The size of the windows controls the size of the Jacobian matrices
$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
Thus, using smaller windows will reduce the amount of computer memory needed to
fit the source coefficients.
Nevertheless, smaller windows may produce less accurate predictions because
their inability to achieve the global minimum of the misfit from
equation~\ref{eq:misfit-unscaled}.
Besides, the window size might also impact on the computation time needed to
fit the source coefficients: smaller windows will generate simpler least-square
problems which are easier to solve, but they will also create more iterations.

We want to assess how the size of the overlapping windows impacts both the
accuracy of the predictions and the computation time needed to fit the source
coefficients in comparison with the performance of the non-boosted equivalent
sources.

We applied the gradient boosted equivalent sources to interpolate the synthetic
airborne survey on the same points of the target grid.
We selected several window sizes to assess how accuracy and performance depend
on that variable.
For each window size we gridded the synthetic data using block-averaged sources
with a spacing of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
a relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
of 50\%, and with different values of damping.
Then we compared the resulting interpolations with the target grid in order to
get the best prediction for each window size and the damping value used to
obtain it.

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients (see Fig.~\ref{fig:gradient-boosted-comparison}a).
In order to avoid any errors introduced by the way windows are shuffled, the
RMS for each window size was obtained as the mean RMS achieved by using
different random seeds.

We have also registered the computational time needed to fit the
gradient-boosted equivalent sources for each window size and computed the ratio
between these times and the computational time needed to fit the non-boosted
equivalent sources (see Fig.~\ref{fig:gradient-boosted-comparison}b).

From the results obtained from the comparison with the synthetic airborne
survey we can conclude that smaller windows generate less accurate predictions
than using larger ones and require significantly more computational time to fit
the sources.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows gets larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
For very large windows, both accuracy and fitting time are almost constant.

In comparison with the non-boosted equivalent sources, we can see that the
gradient-boosted ones produce slightly less accurate results due to not being
able to achieve the global minimum of the least-squares problem, but they
perform faster.

When using gradient-boosted equivalent sources we can conclude that we want to
maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

@@

>>>>

\begin{equation}
    \left[
      \mathbf{B}\trans \mathbf{W} \mathbf{B} + \lambda \mathbf{I}
    \right]
    \hat{\mathbf{m}} =
    \mathbf{B}\trans\mathbf{W}
    \mathbf{d}^o.
    \label{eq:least_squares_solution}
\end{equation}

@@

\subsection{Source distribution strategies}

@@

\subsection{Window size and overlap in gradient boosting}

We assessed the trade-offs in interpolation accuracy and computation time of
the gradient-boosted equivalent sources algorithm as a function of the two key
controlling factors: the window size and the window overlap.
The comparisons were performed against a regular least-squares solution
(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
(Fig.~\ref{fig:synthetic-layouts}c-d) .
To avoid biasing the results, we used the same locations of equivalent sources
for both the regular and gradient-boosted interpolations, namely
block-averaged-sources with a block size of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.

@@

The size of the windows controls the size of the Jacobian matrices
$\tilde{\mathbf{A}}_k$ by limiting the number of data points and equivalent
sources used in each step of the gradient-boosting algorithm
(Alg.~\ref{alg:gradient_boosting_window}).
Thus, using smaller windows will reduce the total amount of computer memory
required to estimate the source coefficients.
Nevertheless, smaller windows may produce less accurate interpolations by
failing to achieve the global minimum of the goal function in
Eq.~\ref{eq:misfit}.
The window size might also impact the computation time in non-intuitive ways
since smaller windows generate smaller least-squares problems but also require
more gradient-boosting iterations.

We calculated the interpolation RMS error and computation time for a fixed
window overlap of 50\% and several window sizes.
To avoid any biases introduced by the shuffling of windows, the calculations
were repeated using different seeds for the pseudo-random number generator used
in the shuffling.
Figs.~\ref{fig:gradient-boosted-comparison}a and
\ref{fig:gradient-boosted-comparison}c show the RMS error and computation time
required for estimating the source coefficients, respectively, as a function of
the window size.

The results show that the interpolation RMS error for gradient-boosting is
generally larger than the error for regular equivalent sources.
The error decreases asymptotically to within $\sim 40\%$ of the regular
equivalent sources for windows with an area greater than $\sim 35\%$ of the
survey area.
The computation time similarly decreases with window size, with the
gradient-boosting being generally faster than the regular equivalent sources
for windows with an area greater than $\sim 20\%$ of the survey area.
As the window size increases, both RMS error and computation time appear to
stabilize to nearly constant levels.

@@

Window size:

In comparison with the non-boosted equivalent sources, we can see that the
gradient-boosted ones produce slightly less accurate results due to not being
able to achieve the global minimum of the least-squares problem, but they
perform faster.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows gets larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
When using gradient-boosted equivalent sources we can conclude that we want to
maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.
